---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# regverse

<!-- badges: start -->
[![R-CMD-check](https://github.com/WangLabCSU/regverse/actions/workflows/R-check.yaml/badge.svg)](https://github.com/WangLabCSU/regverse/actions/workflows/R-check.yaml)
[![Hits](https://hits.seeyoufarm.com/api/count/incr/badge.svg?url=https%3A%2F%2Fgithub.com%2FShixiangWang%2Fregverse&count_bg=%2379C83D&title_bg=%23555555&icon=&icon_color=%23E7E7E7&title=hits&edge_flat=false)](https://hits.seeyoufarm.com)

<!-- badges: end -->

The goal of regverse is to provides R6 classes, methods and utilities to construct,
analyze, summarize, and visualize regression models (CoxPH and GLMs).

## Installation

You can install the development version of regverse like so:

```r
remotes::install_github("WangLabCSU/regverse")
```

## Simple case

This is a basic example which shows you how to build and visualize a Cox model.

Prepare data:

```{r}
library(regverse)
library(survival)

lung <- survival::lung
lung$sex <- factor(lung$sex)
```
Create a model:

```{r}
model <- REGModel$new(
  lung,
  recipe = list(
    x = c("age", "sex"),
    y = c("time", "status")
  )
)

model
```

You can also create it with formula:

```{r}
model <- REGModel$new(
  lung,
  recipe = Surv(time, status) ~ age + sex
)

model
```

Take a look at the model result (package `see` is required):

```{r, fig.width=4, fig.width=6}
model$plot()
```

Visualize with more nice forest plot.

```{r dpi=300}
model$get_forest_data()
model$plot_forest()
```

## Batch processing models

For building a list of regression model, unlike above, a lazy building approach
is used, i.e., `$build()` must manually typed after creating `REGModelList` object.
(This also means you can check or modify the setting before building if necessary)

```{r dpi=300}
ml <- REGModelList$new(
  data = mtcars,
  y = "mpg",
  x = c("factor(cyl)", colnames(mtcars)[3:5]),
  covars = c(colnames(mtcars)[8:9], "factor(gear)")
)
ml
ml$build(f = "gaussian")
str(ml$result)
str(ml$forest_data)

ml$plot_forest(ref_line = 0, xlim = c(-15, 8))
```

## Coverage

```{r}
covr::package_coverage()
```

## LICENSE

(Apache License) Copyright (c) 2025 Shixiang Wang & WangLabCSU team

